\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-04 lang-design.tex
Reply comments.

These two examples both show the incompatibility between exposing the
concrete definition of a field for reasoning (this second example even
involves the definition of fixpoint and pattern matching) and
overridability. We need to be careful about this tension when designing
the language.\YZ{
  The two examples seem to suggest there should not be any overriding allowed at all.
  Is there an example where you actually want the ability to override?
}

>>>>

Note we cannot simply just abandon overriding because we do want it sometimes---say we want a monotonic function \mintinline{Coq}{{.. f := .. ; p : monotonic f; ..}}. The proof of "p" likely requires the concrete definition of "f" but in the future we might want to override "f" and "p" together to swap the definition.

These three examples both show the incompatibility between exposing the
concrete definition of a field for reasoning (this second example even
involves the definition of fixpoint and pattern matching) and
overridability. We need to be careful about this tension when designing
the language.\YZ{
  The two examples seem to suggest there should not be any overriding allowed at all.
  Is there an example where you actually want the ability to override?
}
